Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-12-08 parts/example.tex
typos/errors

@@

The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
\footnote{Files are available at
\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
Then, we verified the reachability for the independent activation of 4 outputs of the signalling
cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD45, CD28, TCRlib) using our
new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
previously defined reachability over-approximation \cite{PMR12-MSCS} (answering either \emph{no} or
\emph{inconclusive}).
All result in conclusive decisions, and the under-approximation has been satisfied in 12 cases (over
32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
(and non-satisfiability in the other cases).

>>>>

\todo{Le résultat peut être raffiné avec l'atteignabilité successive}

@@

The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
\footnote{Files are available at
\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
Then, we verified the reachability for the independent activation of 4 outputs of the signalling
cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD4, CD28, TCRlig) using our
new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
previously defined reachability over-approximation \cite{PMR12-MSCS} (answering either \emph{no} or
\emph{inconclusive}).
All result in conclusive decisions, and the under-approximation has been satisfied in 12 cases (over
32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
(and non-satisfiability in the other cases).

### 2014-12-08 parts/models-ph-php.tex
typos/errors

In \pref{def:fop}, we define the the operator $\Fopsymbol$ which characterises the playability of an action
given the semantics of PH (\pref{def:play}).
This operator considers the \emph{virtual hitters} of an action,
which are the sub-states given by $\csState$ to activate the hitter of the given action if it is a process of cooperative sort.
Furthermore, the target of the action is not taken into account as it is not needed for the rest of the flattening.
%
\begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
  \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters(h) \wedge
    \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\n < \prio(h)}}
    \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
  where if we note $\hitter{h} = a_i$, then:
  \[\virtualhitters(h) =
    \begin{cases}
      a_i & \text{if } a \in \components \text{ or } h \in \ov{\PHh}^{(1)} \\
      \bigvee_{ps \in \csState(a_i)} \left( \bigwedge_{p \in ps} p \right) & \text{if } a \in \cs
    \end{cases}\]
\end{definition}
%
By construction of this operator and given the dynamics of a PH model,
an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.

@@

\paragraph{Removal of the unnecessary cooperative sorts}
There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattening:
\begin{itemize}
  \item if $\Fop{h} \equiv \top$, then the action $h$ can be translated as an auto-action
    (as it is always playable if the target is present);
  \item if the $i$\textsuperscript{th} conjunction of $\Fop{h}$ consists of only one element $p$,
    then $h$ can be translated as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ instead of a cooperative sort
    (as, apart from the target, only one process is required).
\end{itemize}

>>>>

In \pref{def:fop}, we define the the operator $\Fopsymbol$ which characterises the playability of an action
given the semantics of PH (\pref{def:play}).
This operator considers the \emph{virtual hitters} of an action,
which are the sub-states given by $\csState$ to activate the hitter of the given action if it is a process of cooperative sort.
Furthermore, the target of the action is not taken into account as it is not needed for the rest of the flattening.
%
\begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
  \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters(h) \wedge
    \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\\modMF{1 <} n < \prio(h)}}
    \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
  where if we note $\hitter{h} = a_i$, then:
  \[\virtualhitters(h) =
    \begin{cases}
      a_i & \text{if } a \in \components \text{ or } h \in \ov{\PHh}^{(1)} \\
      \bigvee_{ps \in \csState(a_i)} \left( \bigwedge_{p \in ps} p \right) & \text{if } a \in \cs
    \end{cases}\]
\end{definition}
%
By construction of this operator and given the dynamics of a PH model,
an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.

@@

\paragraph{Removal of the unnecessary cooperative sorts}
There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattening:
\begin{itemize}
  \item if $\Fop{h} \equiv \top$, then the action $h$ can be translated as an auto-action
    (as it is always playable if the target is present);
  \item if the $i$\textsuperscript{th} conjunction of $\Fop{h}$ consists of only one element $p$,
    then \modMF{this conjunction} can be translated as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ instead of a cooperative sort
    (as, apart from the target, only one process is required).
\end{itemize}
